Visually pleasing knot projections

### 2021-09-14 inst/jma_knot.tex
fixes #31
fixes #26

Object~{\tt k76} is stored as an object of class {\tt inkscape}: a
two-column matrix with rows corresponding to the node and handle
positions of the inkscape path.  This representation has a certain
amount of redundancy as knot paths have handles which are
symmetrically placed with respect to nodes; also, the first node is
the same as the last for the loop is closed.  The package can coerce
inkscape objects to other forms, specifically {\tt minobj} objects,
which contain no redundancy (the position of each node, as well as one
of the handles, is stored); or {\tt controlpoints} objects, which
allow for easy construction of Bezier interpolation between nodes.

@@

Consider knot~$5_1$. This knot has fivefold rotational symmetry, in
addition to a vertical line of symmetry.  The package includes
functionality to impose appropriate symmetry constraints. Using
Figure~\ref{k5_1_twoknots} as reference, we have:

>>>>

Object~{\tt k76} is stored as an object of class {\tt inkscape}: a
two-column matrix with rows corresponding to the node and handle
positions of the inkscape path.  Above we see only the first six lines
of the object.  Inkscape representation has a certain amount of
redundancy as knot paths have handles which are symmetrically placed
with respect to nodes; also, the first node is the same as the last
for the loop is closed.  The package can coerce inkscape objects to
other forms, specifically {\tt minobj} objects, which contain no
redundancy (the position of each node, as well as one of the handles,
is stored); or {\tt controlpoints} objects, which allow for easy
construction of Bezier interpolation between nodes.

@@

Consider knot~$5_1$. This knot has $D_5$ symmetry with five mirror
lines.  The package includes functionality to impose appropriate
symmetry constraints. Using Figure~\ref{k5_1_twoknots} as reference,
we have:
